Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
wording

The API is designed to adhere to the following broad principles:
\begin{description}
  \item[Inspectability.]
       Constructor parameters
       and parameter values determined by learning algorithms
       are stored as public attributes. All of them are documented in a consistent manner.
       % Gilles: Do we really need to bother the reader with such details?
       % (The Python language does not actually distinguish
       % between public and private attributes of objects,
       % but by convention, any identifier
       % prefixed with an underscore (\texttt{\_})
       % is considered ``a non-public part of the API''; \citealp{pythontut}.)
  \item[Non-proliferation of classes.]
       Learning algorithms are objects of custom classes,
       but datasets and hyperparameter names and values
       are represented as standard Python, NumPy or SciPy classes
       rather than new ones whenever feasible.
       % Gilles: I don't understand the phrase below
       % Custom classes adhere to Python conventions and protocols
       % for constructs such as iteration over the folds
       % in a $k$-fold cross validation.
       This should keep \sklearn easy to use
       and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  \item[Composition.]
       Many machine learning tasks are expressible
       as \textit{pipelines} of transformations to data.
       Also, some learning algorithms are naturally viewed
       as meta-algorithms parameterized on other algorithms.
       To be able to implement and use these algorithms in a simple way,
       all learners are usable with a consistent set of methods
       and a simple syntax is implemented
       for setting/retrieving parameters of sub-estimators.
       % XXX need to describe this!
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default and appropriate value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

@@

The public API is oriented towards batch processing. While classification and
regression algorithms can make predictions for single samples, most \sklearn
algorithms are intended to be used on batches of data. For efficiency reasons,
this indeed makes the use of NumPy and SciPy optimal by preventing the overhead
inherent to Python function calls and to per-element dynamic type checking.
% Gilles: I don't think it is worth elaborating too much (if at all) on online learning. They are exceptions in scikit-learn.

@@

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
normalization, feature selection, learning and making predictions). A sequence
of $N$ such steps can be combined into a composite object called a
\texttt{Pipeline}. The first $N-1$ steps must be transformers and the last can
be either a predictor or a transformer. Conceptually, fitting a pipeline to a
training set amounts to the following recursive procedure: i) when only one step
remains, call its \texttt{fit} method; ii) otherwise, fit the first step, use it
to \texttt{transform} the training set and fit the rest of the pipeline with the
transformed data.

The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can itself be used as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer. \textcolor{red}{TODO:
Talk about nested attribute syntax.}

>>>>

The API is designed to adhere to the following broad principles:
\begin{description}
  \item[Inspectability.]
       Constructor parameters
       and parameter values determined by learning algorithms
       are stored as public attributes. All of them are documented in a consistent manner.
       % Gilles: Do we really need to bother the reader with such details?
       % (The Python language does not actually distinguish
       % between public and private attributes of objects,
       % but by convention, any identifier
       % prefixed with an underscore (\texttt{\_})
       % is considered ``a non-public part of the API''; \citealp{pythontut}.)
  \item[Non-proliferation of classes.]
       Learning algorithms are objects of custom classes,
       but datasets and hyperparameter names and values
       are represented as standard Python, NumPy or SciPy classes
       rather than new ones whenever feasible.
       % Gilles: I don't understand the phrase below
       % Custom classes adhere to Python conventions and protocols
       % for constructs such as iteration over the folds
       % in a $k$-fold cross validation.
       This should keep \sklearn easy to use
       and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  \item[Composition.]
       Many machine learning tasks are expressible
       as \textit{pipelines} of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parameterized on other algorithms.
       To be able to implement and use these algorithms in a simple way,
       all learners are usable with a consistent set of methods
       and a simple syntax is implemented
       for setting and retrieving parameters of sub-estimators.
       % XXX need to describe this!
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default and appropriate value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

@@

The public API is oriented towards batch processing. While classification and
regression algorithms can indeed make predictions for single samples, most \sklearn
objects are however intended to be used on batches of data. For efficiency reasons,
this indeed makes the use of NumPy and SciPy optimal by preventing the overhead
inherent to Python function calls and per-element dynamic type checking.
% Gilles: I don't think it is worth elaborating too much (if at all) on online learning. They are exceptions in scikit-learn.

@@

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
normalization, feature selection, learning and making predictions). A sequence
of $N$ such steps can be combined into a composite object called a
\texttt{Pipeline}. The first $N-1$ steps must be transformers and the last can
be either a predictor or a transformer. Conceptually, fitting a pipeline to a
training set amounts to the following recursive procedure: i) when only one step
remains, call its \texttt{fit} method; ii) otherwise, fit the first step, use it
to \texttt{transform} the training set and fit the rest of the pipeline with the
transformed data.
The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can itself be used as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer. \textcolor{red}{TODO:
Talk about nested attribute syntax.}
